Examination of shapes! (homework exam)

### 2016-02-19 geometricAlgorithms/homeworkExam/homeworkExam.tex
question 1A

% TODO: wtf?
So there existions a quaternion $\exists q \in Q$ where there is an $xy$-silhoeutte
$s$ that is not equal to any other sillhoute.

So an $xy$ sillhouette is unique if there is no repitition in the outer plan that
can be reshown trough rotation.

Although it does have to be notated that you can always flip the entire thing 180
degree and receive the exact sam sillhoutte.

\subsubsection{When it is not unique}
%TODO: \dots
\subsection{Give an algorithm that detrmines an $xy$-silhouette of a conves polyhedron $P$ in O(n) time}
\begin{algorithmic}
	\State Sort all line segment $s \in S$ end points $p$ based on
		$y$ coordinate.
		$p$ should have a reference to its coorisponding point (ie the start
		point has a reference to the end point and vice versa). The resulting
		collection is called $E_{sorted}$
	\For{point$\in E_{sorted}$}
		\State
		\If{begin point} insert in State. On inserted point calculate
		if there is a crossing if so insert in $E_{sorted}$.
		\EndIf
		\If{end point} remove begin point from state.
		\EndIf
		\If{Crossing point} add to result.
		\EndIf
	\EndFor
\end{algorithmic}

>>>>

So when projecting a polyhedron P on an $xy$ plane (ie removing the z values).
you need to have 3 angles. $x$ rotation, $y$ rotation and $z$ rotation.

An $xy$-silhoutte is said to be unique if there is only one set of rotations
that can generate that sillhouette.

I had initially some questions about this defintion, because is it not possible
to always generate another sillouthe by just applying enough rotations.
So I started drawing a simple sillhoutte, a square with an angle.

\begin{figure}
\begin{tikzpicture}[
rotor/.style={inner sep=3pt,outer sep=0,fill opacity=0.3,minimum width=2cm,circle},
crossline/.style={gray,line width=3pt,opacity=0.5,line cap=round}
]
	\node[rotor] (n2) at (4,2)  {\quad y};

	\draw [->,line width=1pt] (n2) ++(140:5mm) arc (-220:40:5mm);
	\draw (1,1) -- (3,1) -- (3,3) -- (1,3) -- (1,1);
	\draw (2,2) -- (0,2) -- (0,1);

	\draw (5,1) -- (7,1) -- (7,3) -- (5,3) -- (5,1);
	\draw (6,2) -- (8,2) -- (8,1);

	\draw (4,0) -- (4,4);
\end{tikzpicture}
\caption{Cube with arm sticking out sillhoutte}
\end{figure}

I did applied similiar rotations for the $x$ and $z$ axis. If you
do both 180 degrees you end up looking at the same side. So for this
particiluar figure there exists a unique $xy$-sillhoutte.

\subsubsection{When it is not unique}

It is not unique when certain parts of the figure can be mirrored. For
example consider the follwoing figure:

\begin{figure}
\begin{tikzpicture}[
rotor/.style={inner sep=3pt,outer sep=0,fill opacity=0.3,minimum width=2cm,circle},
crossline/.style={gray,line width=3pt,opacity=0.5,line cap=round}
]
	\node[rotor] (n2) at (5,2)  {\quad y};

	\draw [->,line width=1pt] (n2) ++(140:5mm) arc (-220:40:5mm);
	\draw (1,1) -- (3,1) -- (3,3) -- (1,3) -- (1,1);
	\draw (2,2) -- (0,2) -- (0,1);
	\draw (2,2) -- (4,2) -- (4,3);

	\draw (7,1) -- (9,1) -- (9,3) -- (7,3) -- (7,1);
	\draw (8,2) -- (10,2) -- (10,1);
	\draw (8,2) -- (6,2) -- (6,3);

	\draw (5,0) -- (5,4);
\end{tikzpicture}
\caption{Cube with two arms in opposite direction sillhoutte}
\end{figure}

The issue with this figue is that if you apply 180 degrees $z$ rotation you
end up with the same sillhoutte. So having some symetry ends up causing will
cause having redundant sillhouttes.

\subsection{Give an algorithm that detrmines an $xy$-silhouette of a conves polyhedron $P$ in O(n) time}
\begin{algorithmic}
	\State Sort all line segment $s \in S$ end points $p$ based on
		$y$ coordinate.
		$p$ should have a reference to its coorisponding point (ie the start
		point has a reference to the end point and vice versa). The resulting
		collection is called $E_{sorted}$
	\For{point$\in E_{sorted}$}
		\State
		\If{begin point} insert in State. On inserted point calculate
		if there is a crossing if so insert in $E_{sorted}$.
		\EndIf
		\If{end point} remove begin point from state.
		\EndIf
		\If{Crossing point} add to result.
		\EndIf
	\EndFor
\end{algorithmic}
